### 2020-07-22 eda.Rmd
Update before last class

* Remake table 6 with bootstrapped standard errors
* Remake table 7 with kernel density estimators and compare with the percentiles percentiles from the quantile regression
* Estimate the proportion of people who would open an account
* Do a k-sample test to compare the savings or change in svaings of the three groups. Then do pair-wise tests with corrections for multiple testing. 
* We can use LOESS/KDE to compare any of the bivariate relationships
    * Year of education by totbal or change in totbal
    * Age or age2 by totbal or change in totbal

>>>>

* Remake table 6 with nonparametric regression techniques. To deal with outliers, they do a bunch of probits for specific thresholds. 
* Remake table 7 with kernel density estimators and compare with the percentiles percentiles from the quantile regression
* Estimate the proportion of people who would open an account
* Do a k-sample test to compare the savings or change in svaings of the three groups. Then do pair-wise tests with corrections for multiple testing. 
* We can use LOESS/KDE to compare any of the bivariate relationships
    * Year of education by totbal or change in totbal
    * Age or age2 by totbal or change in totbal
